Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-24 ms.tex
added sentence reiterating that 2015 release updates did not materially improve zodiacal light problem

\begin{figure*}
\begin{center}
\epsfig{file=fig/results.eps, width=7.0in}
\caption{\label{fig:results} (top) Hot dust temperature derived from our
full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD
100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky
map of best-fit two-component 545 GHz optical depth.}
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\epsfig{file=fig/results.eps, width=7.0in}
\caption{\label{fig:results} (top) Hot dust temperature derived from our
full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD
100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky
map of best-fit two-component 545 GHz optical depth. Note that the 
prominent imprint of the zodiacal light on the dust temperature map has not
been reduced/changed significantly relative to the \cite{meisner15} 
results based on the \PLANCK~2013 data release maps.}
\end{center}
\end{figure*}
